### 2023-04-21 Manuscript/Draft1.tex
update manuscript

Figure \ref{fig:PopPct} depicts the spatial shifting that occurs in each stratum within our population models, specifically during the bottom trawl survey weeks in the spring (13 and 14) and fall (37 and 28). The left column depicts the percent of population that exists in each stratum for each species when the temperature is a constant repeating pattern. In these scenarios we notice a small amount of shifting between successive years as the population aggregates on hot spots in the domain. On the other hand, in the right column where the temperature is increasing over time we note significant shifting taking places in certain strata. This figure shows how we were able to mimic shifting distributions due to climate change by running simulations with a temperature gradient that increased on average over time.

Tables \ref{tab:YTresultsallstrata}, \ref{tab:YTresultsreducedstrata}, \ref{tab:CodERROR}, and \ref{tab:HadERROR} contain the results of our comparison between the absolute error between abundance estimates and model output. While the model-based results tended to provide a lower relative error to the stratified mean with a mean relative error of 0.34 compared to 0.38, the model-based estimates were very sensitive to the settings used. As a result, although \(132/160=82.5\%\) of individual scenarios had a VAST estimate with a lower relative error than the corresponding stratified mean estimate, the variance for the VAST errors was much larger than the stratified mean (0.10 compared to 0.02). VAST models that include covariate information provided the lowest overall errors and standard deviations. When we reduce the number of strata that are included in indexing calculations to simulate species shifting into new territory, we typically see an increase in absolute error (as expected), though there are some scenarios where the impact is minimal. Furthermore, there are scenarios where including covariates in VAST models actually increases the absolute error, especially when we fail to sample the entire domain.

@@

In considering the Yellowtail Flounder results in Tables \ref{tab:YTresultsallstrata} and \ref{tab:YTresultsreducedstrata}, we can see VAST estimates generally provide lower errors relative to those derived from the stratified mean, with models that include covariate information typically providing the lowest errors. When all strata are sampled, adding covariates greatly improved estimates in all scenarios. We still see an improvement in VAST estimates when certain strata are excluded from sampling, but the improvement was much less dramatic than with all strata included. However, there are several instances in which VAST failed to provide improved abundance estimates during the fall season without covariate information, producing the largest errors seen in Tables \ref{tab:YTresultsallstrata} and \ref{tab:YTresultsreducedstrata}. Each of these instances are These errors are corrected by including covariate information resulting in improved VAST estimates that are significantly lower than their stratified mean counterparts.

Including detailed covariate information made a noticeable difference in our Yellowtail Flounder model-based VAST estimates. All of the VAST estimates that included covariate information produced a lower relative error than the corresponding VAST model that did not include covariates. The largest improvements were seen in the increasing temperature scenarios. As a result, of the VAST estimates that included covariates information, \(47/48\approx98\)\% had a lower relative error than the corresponding stratified mean estimate. This implies that the covariate information helped our model-based estimate account for the design-based issues related to small strata that contain a large percentage of the population, which can become exacerbated in the increasing temperature scenario.

The performance of our abundance estimates tend to decrease under increasing temperature, with the most dramatic changes seen in our VAST estimates without covariates. One exception to this is when we use a stratified mean approach while the population is decreasing. Our analyses have found that the stratified mean tends to under estimate the true abundance and since these estimates are bounded below by zero, as the Yellowtail population decreases towards zero the difference between the estimate and the true value also decrease. That is, if the population is low enough, failing to appropriately sample the population in a design-based method produces the same result as appropriately sampling.

\textbf{For discussion: clearly our perfect covariate information made a big difference here, but the question is could we achieve similar results without ``perfect'' information? Which covariate is best? Good question for future research}

We see a seasonal impact of an increasing average temperature in stratum 16 in the Cod results in Figure \ref{fig:PopPct}. In the constant temperature scenario for Cod, in both seasons the population is decreasing its presence in strata 19 and 20 over the duration of the simulation, while simultaneously increasing presence in stratum 16. However, an increase in average temperature in the fall drives the population out of strata 16 and 21, and into 18, 22, and 24 (see Figure \ref{fig:hab-plot}). Similar to the Yellowtail Flounder population, stratum the habitat in stratum 16 acts as an attractor in both temperature scenarios in the spring when the water temperature is cooler. When the temperature increases over time the fall population begins to prefer the adjacent strata that are deeper and/or more northern than stratum 16.

(see Table \ref{tab:CodERROR}) In the Cod results, when using reduced strata in constant temperature, adding covariates produces worse VAST results (though still better than stratified mean). This is similar to what we see with all of Haddock results (adding covariates makes it worse with reduced strata). This is NOT seen with Yellowtail (adding covariates always helps). VAST without covariates much worse than stratified mean in fall with increasing temperature, but adding covariates corrects this and makes VAST estimates better than stratified mean.

Of the abundance estimates without covariates, \(12/16=75\)\% had a VAST fit with a lower relative error compared to the stratified mean estimate. Including detailed covariate information in our Cod VAST estimates resulted in all \(16/16=100\%\) having a lower relative error than the corresponding stratified mean estimate. The 4 scenarios without covariates that had a higher VAST error were each overestimates for the fall season that involved an increasing temperature gradient. Similar to Yellowtail Flounder results, Cod are shifting their spatial distribution into the smaller exterior strata in these conditions, which is decreasing the accuracy of the covariate-free VAST estimate. While adding covariates to these fits allowed for an improved error relative to the stratified mean, the VAST abundance still display an overestimate early in the time series before covariates correct the trend, allowing for a lower overall absolute error \textbf{(show these plots? IncTemp fall scenarios)}.

(see Table \ref{tab:HadERROR}) For Haddock, VAST has a particularly hard time in spring regularly producing larger errors than the stratified mean with added covariates only improving to the level of the stratified mean. VAST shows improved results in fall relative to the stratified mean with added covariates producing extremely low errors in some cases. In Haddock results, adding covariates improves estimates only when all strata are included (when reduced strata, adding covariates actually makes VAST worse). Since this occurs in all scenarios, it seems to again be related to failing to accurately monitor strata 17.

\(10/16\approx63\)\% of the scenarios without covariates had a VAST fit with a lower relative error compared to the stratified mean estimate. The 6 covariate-free VAST estimates that resulted in a higher error than the stratified mean spanned all scenarios and seasons, with several fall errors being especially large (significant overestimates). Adding covariate information resulted in \(14/16\approx88\)\% of VAST estimates having improved error compared to the stratified mean. The 2 scenarios that procedure worse error spanned temperature scenarios, but were both in the spring season when the proportion of the population in each strata remained constant in each scenario.\textbf{why?? doesnt make sense. the values with cov are about the same as SM} Qualitatively, including covariate information has a larger impact on decreasing the relative error compared to the stratified mean compared to failing to include covariates.

@@

@@

Table 1. Parameters used in all population models. SAW 1: (NEFSC 2012), SAW 2: (NEFSC 2013), SAW 3: ???

@@

\cellcolor[HTML]{A4A4A4}{\textcolor{white}{\textbf{\hspace{1em}Constant}}} & \cellcolor[HTML]{A4A4A4}{\textcolor{white}{\textbf{spring}}} & \cellcolor[HTML]{A4A4A4}{\textcolor{white}{\textbf{w/ cov}}} & \cellcolor[HTML]{A4A4A4}{\textcolor{white}{\textbf{no}}} & \cellcolor[HTML]{A4A4A4}{\textcolor{white}{\textbf{0.07}}} & \cellcolor[HTML]{A4A4A4}{\textcolor{white}{\textbf{0.07}}} & \cellcolor[HTML]{A4A4A4}{\textcolor{white}{\textbf{0.21}}}\\

@@

\cellcolor[HTML]{D2D2D2}{\textcolor{white}{\textbf{\hspace{1em}Constant}}} & \cellcolor[HTML]{D2D2D2}{\textcolor{white}{\textbf{spring}}} & \cellcolor[HTML]{D2D2D2}{\textcolor{white}{\textbf{w/ cov}}} & \cellcolor[HTML]{D2D2D2}{\textcolor{white}{\textbf{yes}}} & \cellcolor[HTML]{D2D2D2}{\textcolor{white}{\textbf{0.08}}} & \cellcolor[HTML]{D2D2D2}{\textcolor{white}{\textbf{0.08}}} & \cellcolor[HTML]{D2D2D2}{\textcolor{white}{\textbf{0.25}}}\\

@@

\cellcolor[HTML]{A4A4A4}{\textcolor{white}{\textbf{\hspace{1em}Constant}}} & \cellcolor[HTML]{A4A4A4}{\textcolor{white}{\textbf{fall}}} & \cellcolor[HTML]{A4A4A4}{\textcolor{white}{\textbf{w/ cov}}} & \cellcolor[HTML]{A4A4A4}{\textcolor{white}{\textbf{no}}} & \cellcolor[HTML]{A4A4A4}{\textcolor{white}{\textbf{0.14}}} & \cellcolor[HTML]{A4A4A4}{\textcolor{white}{\textbf{0.08}}} & \cellcolor[HTML]{A4A4A4}{\textcolor{white}{\textbf{0.32}}}\\

@@

\cellcolor[HTML]{D2D2D2}{\textcolor{white}{\textbf{\hspace{1em}Constant}}} & \cellcolor[HTML]{D2D2D2}{\textcolor{white}{\textbf{fall}}} & \cellcolor[HTML]{D2D2D2}{\textcolor{white}{\textbf{w/ cov}}} & \cellcolor[HTML]{D2D2D2}{\textcolor{white}{\textbf{yes}}} & \cellcolor[HTML]{D2D2D2}{\textcolor{white}{\textbf{0.17}}} & \cellcolor[HTML]{D2D2D2}{\textcolor{white}{\textbf{0.11}}} & \cellcolor[HTML]{D2D2D2}{\textcolor{white}{\textbf{0.31}}}\\

@@

\cellcolor[HTML]{A4A4A4}{\textcolor{white}{\textbf{\hspace{1em}Increasing}}} & \cellcolor[HTML]{A4A4A4}{\textcolor{white}{\textbf{spring}}} & \cellcolor[HTML]{A4A4A4}{\textcolor{white}{\textbf{w/ cov}}} & \cellcolor[HTML]{A4A4A4}{\textcolor{white}{\textbf{no}}} & \cellcolor[HTML]{A4A4A4}{\textcolor{white}{\textbf{0.05}}} & \cellcolor[HTML]{A4A4A4}{\textcolor{white}{\textbf{0.06}}} & \cellcolor[HTML]{A4A4A4}{\textcolor{white}{\textbf{0.28}}}\\

@@

\cellcolor[HTML]{D2D2D2}{\textcolor{white}{\textbf{\hspace{1em}Increasing}}} & \cellcolor[HTML]{D2D2D2}{\textcolor{white}{\textbf{spring}}} & \cellcolor[HTML]{D2D2D2}{\textcolor{white}{\textbf{w/ cov}}} & \cellcolor[HTML]{D2D2D2}{\textcolor{white}{\textbf{yes}}} & \cellcolor[HTML]{D2D2D2}{\textcolor{white}{\textbf{0.10}}} & \cellcolor[HTML]{D2D2D2}{\textcolor{white}{\textbf{0.12}}} & \cellcolor[HTML]{D2D2D2}{\textcolor{white}{\textbf{0.28}}}\\

@@

\cellcolor[HTML]{5C5E60}{\textcolor{white}{\textbf{\hspace{1em}Increasing}}} & \cellcolor[HTML]{5C5E60}{\textcolor{white}{\textbf{fall}}} & \cellcolor[HTML]{5C5E60}{\textcolor{white}{\textbf{no cov}}} & \cellcolor[HTML]{5C5E60}{\textcolor{white}{\textbf{yes}}} & \cellcolor[HTML]{5C5E60}{\textcolor{white}{\textbf{1.40}}} & \cellcolor[HTML]{5C5E60}{\textcolor{white}{\textbf{1.38}}} & \cellcolor[HTML]{5C5E60}{\textcolor{white}{\textbf{0.50}}}\\

@@

\cellcolor[HTML]{A4A4A4}{\textcolor{white}{\textbf{\hspace{1em}Increasing}}} & \cellcolor[HTML]{A4A4A4}{\textcolor{white}{\textbf{fall}}} & \cellcolor[HTML]{A4A4A4}{\textcolor{white}{\textbf{w/ cov}}} & \cellcolor[HTML]{A4A4A4}{\textcolor{white}{\textbf{no}}} & \cellcolor[HTML]{A4A4A4}{\textcolor{white}{\textbf{0.21}}} & \cellcolor[HTML]{A4A4A4}{\textcolor{white}{\textbf{0.23}}} & \cellcolor[HTML]{A4A4A4}{\textcolor{white}{\textbf{0.51}}}\\

@@

\cellcolor[HTML]{D2D2D2}{\textcolor{white}{\textbf{\hspace{1em}Increasing}}} & \cellcolor[HTML]{D2D2D2}{\textcolor{white}{\textbf{fall}}} & \cellcolor[HTML]{D2D2D2}{\textcolor{white}{\textbf{w/ cov}}} & \cellcolor[HTML]{D2D2D2}{\textcolor{white}{\textbf{yes}}} & \cellcolor[HTML]{D2D2D2}{\textcolor{white}{\textbf{0.30}}} & \cellcolor[HTML]{D2D2D2}{\textcolor{white}{\textbf{0.28}}} & \cellcolor[HTML]{D2D2D2}{\textcolor{white}{\textbf{0.50}}}\\

@@

\cellcolor[HTML]{A4A4A4}{\textcolor{white}{\textbf{\hspace{1em}Constant}}} & \cellcolor[HTML]{A4A4A4}{\textcolor{white}{\textbf{spring}}} & \cellcolor[HTML]{A4A4A4}{\textcolor{white}{\textbf{w/ cov}}} & \cellcolor[HTML]{A4A4A4}{\textcolor{white}{\textbf{no}}} & \cellcolor[HTML]{A4A4A4}{\textcolor{white}{\textbf{0.07}}} & \cellcolor[HTML]{A4A4A4}{\textcolor{white}{\textbf{0.06}}} & \cellcolor[HTML]{A4A4A4}{\textcolor{white}{\textbf{0.23}}}\\

@@

\cellcolor[HTML]{D2D2D2}{\textcolor{white}{\textbf{\hspace{1em}Constant}}} & \cellcolor[HTML]{D2D2D2}{\textcolor{white}{\textbf{spring}}} & \cellcolor[HTML]{D2D2D2}{\textcolor{white}{\textbf{w/ cov}}} & \cellcolor[HTML]{D2D2D2}{\textcolor{white}{\textbf{yes}}} & \cellcolor[HTML]{D2D2D2}{\textcolor{white}{\textbf{0.11}}} & \cellcolor[HTML]{D2D2D2}{\textcolor{white}{\textbf{0.07}}} & \cellcolor[HTML]{D2D2D2}{\textcolor{white}{\textbf{0.27}}}\\

@@

\cellcolor[HTML]{A4A4A4}{\textcolor{white}{\textbf{\hspace{1em}Constant}}} & \cellcolor[HTML]{A4A4A4}{\textcolor{white}{\textbf{fall}}} & \cellcolor[HTML]{A4A4A4}{\textcolor{white}{\textbf{w/ cov}}} & \cellcolor[HTML]{A4A4A4}{\textcolor{white}{\textbf{no}}} & \cellcolor[HTML]{A4A4A4}{\textcolor{white}{\textbf{0.16}}} & \cellcolor[HTML]{A4A4A4}{\textcolor{white}{\textbf{0.08}}} & \cellcolor[HTML]{A4A4A4}{\textcolor{white}{\textbf{0.41}}}\\

@@

\cellcolor[HTML]{D2D2D2}{\textcolor{white}{\textbf{\hspace{1em}Constant}}} & \cellcolor[HTML]{D2D2D2}{\textcolor{white}{\textbf{fall}}} & \cellcolor[HTML]{D2D2D2}{\textcolor{white}{\textbf{w/ cov}}} & \cellcolor[HTML]{D2D2D2}{\textcolor{white}{\textbf{yes}}} & \cellcolor[HTML]{D2D2D2}{\textcolor{white}{\textbf{0.29}}} & \cellcolor[HTML]{D2D2D2}{\textcolor{white}{\textbf{0.18}}} & \cellcolor[HTML]{D2D2D2}{\textcolor{white}{\textbf{0.37}}}\\

@@

\cellcolor[HTML]{A4A4A4}{\textcolor{white}{\textbf{\hspace{1em}Increasing}}} & \cellcolor[HTML]{A4A4A4}{\textcolor{white}{\textbf{spring}}} & \cellcolor[HTML]{A4A4A4}{\textcolor{white}{\textbf{w/ cov}}} & \cellcolor[HTML]{A4A4A4}{\textcolor{white}{\textbf{no}}} & \cellcolor[HTML]{A4A4A4}{\textcolor{white}{\textbf{0.08}}} & \cellcolor[HTML]{A4A4A4}{\textcolor{white}{\textbf{0.07}}} & \cellcolor[HTML]{A4A4A4}{\textcolor{white}{\textbf{0.22}}}\\

@@

\cellcolor[HTML]{D2D2D2}{\textcolor{white}{\textbf{\hspace{1em}Increasing}}} & \cellcolor[HTML]{D2D2D2}{\textcolor{white}{\textbf{spring}}} & \cellcolor[HTML]{D2D2D2}{\textcolor{white}{\textbf{w/ cov}}} & \cellcolor[HTML]{D2D2D2}{\textcolor{white}{\textbf{yes}}} & \cellcolor[HTML]{D2D2D2}{\textcolor{white}{\textbf{0.16}}} & \cellcolor[HTML]{D2D2D2}{\textcolor{white}{\textbf{0.10}}} & \cellcolor[HTML]{D2D2D2}{\textcolor{white}{\textbf{0.26}}}\\

@@

\cellcolor[HTML]{A4A4A4}{\textcolor{white}{\textbf{\hspace{1em}Increasing}}} & \cellcolor[HTML]{A4A4A4}{\textcolor{white}{\textbf{fall}}} & \cellcolor[HTML]{A4A4A4}{\textcolor{white}{\textbf{w/ cov}}} & \cellcolor[HTML]{A4A4A4}{\textcolor{white}{\textbf{no}}} & \cellcolor[HTML]{A4A4A4}{\textcolor{white}{\textbf{0.40}}} & \cellcolor[HTML]{A4A4A4}{\textcolor{white}{\textbf{0.15}}} & \cellcolor[HTML]{A4A4A4}{\textcolor{white}{\textbf{0.28}}}\\

>>>>

Figure \ref{fig:PopPct} depicts the spatial shifting that occurs in each stratum within our population models, specifically during the bottom trawl survey weeks in the spring (13 and 14) and fall (37 and 28). The left column depicts the percent of population that exists in each stratum for each species when the temperature is a constant repeating pattern. In these scenarios we notice a small amount of shifting between successive years as the population aggregates on especially suitable habitat in the domain. More exaggerated shifting takes place in a larger number of strata when the temperature is increasing over time, as seen right column of Figure \ref{fig:PopPct}. This figure demonstrates how we were able to mimic shifting distributions due to climate change by running simulations with a temperature gradient that increased on average over time.

Tables \ref{tab:YTresultsallstrata}, \ref{tab:YTresultsreducedstrata}, \ref{tab:CodERROR}, and \ref{tab:HadERROR} contain the results of our comparison between the absolute error between abundance estimates and model output. While the model-based results tended to provide a lower relative error to the stratified mean with a mean relative error of 0.34 compared to 0.38, the model-based estimates were very sensitive to the settings used. As a result, although \(132/160=82.5\%\) of individual scenarios had a VAST estimate with a lower relative error than the corresponding stratified mean estimate, the variance for the VAST relative errors was much larger than the stratified mean (0.10 compared to 0.02). VAST models that include covariate information provided the lowest overall errors and standard deviations. When we reduce the number of strata that are included in indexing calculations to simulate species shifting into new territory, we typically see an increase in absolute error (as expected), though there are some scenarios where the impact is minimal. Furthermore, there are scenarios where including covariates in VAST models actually increases the absolute error, especially when we fail to sample the entire domain.

In considering the Yellowtail Flounder results in Tables \ref{tab:YTresultsallstrata} and \ref{tab:YTresultsreducedstrata}, we can see VAST estimates generally provide lower errors relative to those derived from the stratified mean, with models that include covariate information typically providing the lowest errors. When all strata are sampled, adding covariates greatly improved estimates in all scenarios. We still see an improvement in VAST estimates when certain strata are excluded from sampling, but the improvement was much less dramatic than with all strata included. However, there are several instances in which VAST failed to provide improved abundance estimates during the fall season without covariate information, producing the largest errors seen in Tables \ref{tab:YTresultsallstrata} and \ref{tab:YTresultsreducedstrata}. Including covariate information to each VAST model produced estimates with significantly lower error than their stratified mean counterparts.

Including covariate information made a noticeable difference in our Yellowtail Flounder model-based VAST estimates. All of the VAST estimates that included covariate information produced a lower relative error than the corresponding VAST model that did not include covariates. The largest improvements were seen in the increasing temperature scenarios. As a result, of the VAST estimates that included covariates information, \(47/48\approx98\)\% had a lower relative error than the corresponding stratified mean estimate. This implies that the covariate information helped our model-based estimate account for the design-based issues related to an increasing percentage of the population entering smaller strata, which can become exacerbated in the increasing temperature simulations.

We see diminished performance of our abundance estimates for Yellowtail under increasing temperature, with the most dramatic changes seen in our VAST estimates without covariates. One exception to this is when we use a stratified mean approach while the population is decreasing. Our analyses have found that the stratified mean tends to under estimate the true abundance and since these estimates are bounded below by zero, as the Yellowtail population decreases towards zero the difference between the estimate and the true value also decrease. That is, if the population is low enough, failing to appropriately sample the population in a design-based method produces the same result as appropriately sampling.

In the constant temperature scenario for Cod, in both seasons the population decreases its presence in strata 19 and 20 over the duration of the simulation, while simultaneously increasing presence in stratum 16. However, we see a seasonal impact in stratum 16 during the increasing average temperature simulations where in the fall the population decrease presence in strata 16 and 21, and increase presence in 18, 22, and 24 (see Figure \ref{fig:hab-plot}). Similar to the Yellowtail Flounder population, the favorable habitat in stratum 16 acts as an attractor in both temperature scenarios in the spring when the water temperature is cooler. When the temperature increases over time, the fall population compensates by shifting their preference to the adjacent strata that are deeper and/or further north than stratum 16.

Table \ref{tab:CodERROR} contains the absolute error between our abundance estimates for Cod and the true model values. Of the abundance estimates without covariates, \(12/16=75\)\% had a VAST fit with a lower relative error compared to the stratified mean estimate. VAST produced higher relative error compared to the stratified mean in scenarios that involved increasing temperature in the fall season without covariates. Similar to the Yellowtail results, this implies the model-based approach had seasonal trouble with populations shifting into smaller strata where fewer samples take place. Providing covariate information in these cases once again helped the model-based approach to provide improved absolute error estimates relative to the stratified mean. However, we see that adding covariates to VAST in the fall produces higher absolute error values when sampling reduced strata in the constant temperature scenario.

Table \ref{tab:HadERROR} contains the absolute error between our abundance estimates for Haddock and the true model values. We notice that the model-based VAST produced particularly large errors in spring compared to the stratified mean, with added covariates only improving to the level of the stratified mean. VAST shows improved results in fall relative to the stratified mean with added covariates producing extremely low errors in some cases. For Haddock results, adding covariates improves estimates only when all strata are included. That is, similar to Cod, when sampling a reduced domain adding covariates actually decreases VAST's accuracy. Since this occurs in all scenarios, it seems to again be related to failing to accurately monitor smaller exterior stratum 17.

Of the scenarios without covariates, \(10/16\approx63\)\% had a VAST fit with a lower relative error compared to the stratified mean estimate. The 6 covariate-free VAST estimates that resulted in a higher error than the stratified mean spanned all scenarios and seasons, with several fall errors being especially large (significant overestimates). Adding covariate information resulted in \(14/16\approx88\)\% of VAST estimates having improved error compared to the stratified mean. The 2 scenarios that procedure worse error spanned temperature scenarios, but were both in the spring season when the proportion of the population in each strata remained constant in each scenario. Qualitatively, including covariate information has a larger impact on decreasing the relative error compared to the stratified mean compared to failing to include covariates.

\emph{Impact of Covariates}

Generally help, but dependent on appropriate covariate response. Yellowtail cases always had appropriate response and thus adding covariates always improved estimates. VAST showed decreased performance with Cod and Haddock when covariates added in fall because covariate response was not fully developed. (show plot comparing good vs bad response)

@@

@@

\textbf{For discussion: clearly our perfect covariate information made a big difference for yellowtail flounder (and others), but the question is could we achieve similar results without ``perfect'' information? Which covariate is best? Good question for future research}

@@

Table 1. Parameters used in all population models. SAW 1: (NEFSC 2012), SAW 2: (NEFSC 2013), SAW 3: not out yet???

@@

\cellcolor[HTML]{A4A4A4}{\textcolor{white}{\textbf{\hspace{1em}Constant}}} & \cellcolor[HTML]{A4A4A4}{\textcolor{white}{\textbf{spring}}} & \cellcolor[HTML]{A4A4A4}{\textcolor{white}{\textbf{w/ cov}}} & \cellcolor[HTML]{A4A4A4}{\textcolor{white}{\textbf{no}}} & \cellcolor[HTML]{A4A4A4}{\textcolor{white}{\textbf{0.07}}} & \cellcolor[HTML]{A4A4A4}{\textcolor{white}{\textbf{0.07}}} & \cellcolor[HTML]{A4A4A4}{\textcolor{white}{\textbf{n/a}}}\\

@@

\cellcolor[HTML]{D2D2D2}{\textcolor{white}{\textbf{\hspace{1em}Constant}}} & \cellcolor[HTML]{D2D2D2}{\textcolor{white}{\textbf{spring}}} & \cellcolor[HTML]{D2D2D2}{\textcolor{white}{\textbf{w/ cov}}} & \cellcolor[HTML]{D2D2D2}{\textcolor{white}{\textbf{yes}}} & \cellcolor[HTML]{D2D2D2}{\textcolor{white}{\textbf{0.08}}} & \cellcolor[HTML]{D2D2D2}{\textcolor{white}{\textbf{0.08}}} & \cellcolor[HTML]{D2D2D2}{\textcolor{white}{\textbf{n/a}}}\\

@@

\cellcolor[HTML]{A4A4A4}{\textcolor{white}{\textbf{\hspace{1em}Constant}}} & \cellcolor[HTML]{A4A4A4}{\textcolor{white}{\textbf{fall}}} & \cellcolor[HTML]{A4A4A4}{\textcolor{white}{\textbf{w/ cov}}} & \cellcolor[HTML]{A4A4A4}{\textcolor{white}{\textbf{no}}} & \cellcolor[HTML]{A4A4A4}{\textcolor{white}{\textbf{0.14}}} & \cellcolor[HTML]{A4A4A4}{\textcolor{white}{\textbf{0.08}}} & \cellcolor[HTML]{A4A4A4}{\textcolor{white}{\textbf{n/a}}}\\

@@

\cellcolor[HTML]{D2D2D2}{\textcolor{white}{\textbf{\hspace{1em}Constant}}} & \cellcolor[HTML]{D2D2D2}{\textcolor{white}{\textbf{fall}}} & \cellcolor[HTML]{D2D2D2}{\textcolor{white}{\textbf{w/ cov}}} & \cellcolor[HTML]{D2D2D2}{\textcolor{white}{\textbf{yes}}} & \cellcolor[HTML]{D2D2D2}{\textcolor{white}{\textbf{0.17}}} & \cellcolor[HTML]{D2D2D2}{\textcolor{white}{\textbf{0.11}}} & \cellcolor[HTML]{D2D2D2}{\textcolor{white}{\textbf{n/a}}}\\

@@

\cellcolor[HTML]{A4A4A4}{\textcolor{white}{\textbf{\hspace{1em}Increasing}}} & \cellcolor[HTML]{A4A4A4}{\textcolor{white}{\textbf{spring}}} & \cellcolor[HTML]{A4A4A4}{\textcolor{white}{\textbf{w/ cov}}} & \cellcolor[HTML]{A4A4A4}{\textcolor{white}{\textbf{no}}} & \cellcolor[HTML]{A4A4A4}{\textcolor{white}{\textbf{0.05}}} & \cellcolor[HTML]{A4A4A4}{\textcolor{white}{\textbf{0.06}}} & \cellcolor[HTML]{A4A4A4}{\textcolor{white}{\textbf{n/a}}}\\

@@

\cellcolor[HTML]{D2D2D2}{\textcolor{white}{\textbf{\hspace{1em}Increasing}}} & \cellcolor[HTML]{D2D2D2}{\textcolor{white}{\textbf{spring}}} & \cellcolor[HTML]{D2D2D2}{\textcolor{white}{\textbf{w/ cov}}} & \cellcolor[HTML]{D2D2D2}{\textcolor{white}{\textbf{yes}}} & \cellcolor[HTML]{D2D2D2}{\textcolor{white}{\textbf{0.10}}} & \cellcolor[HTML]{D2D2D2}{\textcolor{white}{\textbf{0.12}}} & \cellcolor[HTML]{D2D2D2}{\textcolor{white}{\textbf{n/a}}}\\

@@

\cellcolor[HTML]{5C5E60}{\textcolor{white}{\textbf{\hspace{1em}Increasing}}} & \cellcolor[HTML]{5C5E60}{\textcolor{white}{\textbf{fall}}} & \cellcolor[HTML]{5C5E60}{\textcolor{white}{\textbf{no cov}}} & \cellcolor[HTML]{5C5E60}{\textcolor{white}{\textbf{yes}}} & \cellcolor[HTML]{5C5E60}{\textcolor{white}{\textbf{1.40}}} & \cellcolor[HTML]{5C5E60}{\textcolor{white}{\textbf{1.38}}} & \cellcolor[HTML]{5C5E60}{\textcolor{white}{\textbf{0.5}}}\\

@@

\cellcolor[HTML]{A4A4A4}{\textcolor{white}{\textbf{\hspace{1em}Increasing}}} & \cellcolor[HTML]{A4A4A4}{\textcolor{white}{\textbf{fall}}} & \cellcolor[HTML]{A4A4A4}{\textcolor{white}{\textbf{w/ cov}}} & \cellcolor[HTML]{A4A4A4}{\textcolor{white}{\textbf{no}}} & \cellcolor[HTML]{A4A4A4}{\textcolor{white}{\textbf{0.21}}} & \cellcolor[HTML]{A4A4A4}{\textcolor{white}{\textbf{0.23}}} & \cellcolor[HTML]{A4A4A4}{\textcolor{white}{\textbf{n/a}}}\\

@@

\cellcolor[HTML]{D2D2D2}{\textcolor{white}{\textbf{\hspace{1em}Increasing}}} & \cellcolor[HTML]{D2D2D2}{\textcolor{white}{\textbf{fall}}} & \cellcolor[HTML]{D2D2D2}{\textcolor{white}{\textbf{w/ cov}}} & \cellcolor[HTML]{D2D2D2}{\textcolor{white}{\textbf{yes}}} & \cellcolor[HTML]{D2D2D2}{\textcolor{white}{\textbf{0.30}}} & \cellcolor[HTML]{D2D2D2}{\textcolor{white}{\textbf{0.28}}} & \cellcolor[HTML]{D2D2D2}{\textcolor{white}{\textbf{n/a}}}\\

@@

\cellcolor[HTML]{A4A4A4}{\textcolor{white}{\textbf{\hspace{1em}Constant}}} & \cellcolor[HTML]{A4A4A4}{\textcolor{white}{\textbf{spring}}} & \cellcolor[HTML]{A4A4A4}{\textcolor{white}{\textbf{w/ cov}}} & \cellcolor[HTML]{A4A4A4}{\textcolor{white}{\textbf{no}}} & \cellcolor[HTML]{A4A4A4}{\textcolor{white}{\textbf{0.07}}} & \cellcolor[HTML]{A4A4A4}{\textcolor{white}{\textbf{0.06}}} & \cellcolor[HTML]{A4A4A4}{\textcolor{white}{\textbf{n/a}}}\\

@@

\cellcolor[HTML]{D2D2D2}{\textcolor{white}{\textbf{\hspace{1em}Constant}}} & \cellcolor[HTML]{D2D2D2}{\textcolor{white}{\textbf{spring}}} & \cellcolor[HTML]{D2D2D2}{\textcolor{white}{\textbf{w/ cov}}} & \cellcolor[HTML]{D2D2D2}{\textcolor{white}{\textbf{yes}}} & \cellcolor[HTML]{D2D2D2}{\textcolor{white}{\textbf{0.11}}} & \cellcolor[HTML]{D2D2D2}{\textcolor{white}{\textbf{0.07}}} & \cellcolor[HTML]{D2D2D2}{\textcolor{white}{\textbf{n/a}}}\\

@@

\cellcolor[HTML]{A4A4A4}{\textcolor{white}{\textbf{\hspace{1em}Constant}}} & \cellcolor[HTML]{A4A4A4}{\textcolor{white}{\textbf{fall}}} & \cellcolor[HTML]{A4A4A4}{\textcolor{white}{\textbf{w/ cov}}} & \cellcolor[HTML]{A4A4A4}{\textcolor{white}{\textbf{no}}} & \cellcolor[HTML]{A4A4A4}{\textcolor{white}{\textbf{0.16}}} & \cellcolor[HTML]{A4A4A4}{\textcolor{white}{\textbf{0.08}}} & \cellcolor[HTML]{A4A4A4}{\textcolor{white}{\textbf{n/a}}}\\

@@

\cellcolor[HTML]{D2D2D2}{\textcolor{white}{\textbf{\hspace{1em}Constant}}} & \cellcolor[HTML]{D2D2D2}{\textcolor{white}{\textbf{fall}}} & \cellcolor[HTML]{D2D2D2}{\textcolor{white}{\textbf{w/ cov}}} & \cellcolor[HTML]{D2D2D2}{\textcolor{white}{\textbf{yes}}} & \cellcolor[HTML]{D2D2D2}{\textcolor{white}{\textbf{0.29}}} & \cellcolor[HTML]{D2D2D2}{\textcolor{white}{\textbf{0.18}}} & \cellcolor[HTML]{D2D2D2}{\textcolor{white}{\textbf{n/a}}}\\

@@

\cellcolor[HTML]{A4A4A4}{\textcolor{white}{\textbf{\hspace{1em}Increasing}}} & \cellcolor[HTML]{A4A4A4}{\textcolor{white}{\textbf{spring}}} & \cellcolor[HTML]{A4A4A4}{\textcolor{white}{\textbf{w/ cov}}} & \cellcolor[HTML]{A4A4A4}{\textcolor{white}{\textbf{no}}} & \cellcolor[HTML]{A4A4A4}{\textcolor{white}{\textbf{0.08}}} & \cellcolor[HTML]{A4A4A4}{\textcolor{white}{\textbf{0.07}}} & \cellcolor[HTML]{A4A4A4}{\textcolor{white}{\textbf{n/a}}}\\

@@

\cellcolor[HTML]{D2D2D2}{\textcolor{white}{\textbf{\hspace{1em}Increasing}}} & \cellcolor[HTML]{D2D2D2}{\textcolor{white}{\textbf{spring}}} & \cellcolor[HTML]{D2D2D2}{\textcolor{white}{\textbf{w/ cov}}} & \cellcolor[HTML]{D2D2D2}{\textcolor{white}{\textbf{yes}}} & \cellcolor[HTML]{D2D2D2}{\textcolor{white}{\textbf{0.16}}} & \cellcolor[HTML]{D2D2D2}{\textcolor{white}{\textbf{0.10}}} & \cellcolor[HTML]{D2D2D2}{\textcolor{white}{\textbf{n/a}}}\\

@@

\cellcolor[HTML]{A4A4A4}{\textcolor{white}{\textbf{\hspace{1em}Increasing}}} & \cellcolor[HTML]{A4A4A4}{\textcolor{white}{\textbf{fall}}} & \cellcolor[HTML]{A4A4A4}{\textcolor{white}{\textbf{w/ cov}}} & \cellcolor[HTML]{A4A4A4}{\textcolor{white}{\textbf{no}}} & \cellcolor[HTML]{A4A4A4}{\textcolor{white}{\textbf{0.40}}} & \cellcolor[HTML]{A4A4A4}{\textcolor{white}{\textbf{0.15}}} & \cellcolor[HTML]{A4A4A4}{\textcolor{white}{\textbf{n/a}}}\\
